Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-09-25 draftfinalreport_v4.Rnw
adds info about vaccine failures

\begin{figure}[H]
     \begin{center}
     \includegraphics[width=1\textwidth]{nzers.pdf}
     \end{center}
     \caption{Trends in international travel, determined by immigration arrival data and New Zealander travel departure destinations. Note this is for all age categories.}
     \label{fig:travel}
\end{figure}

Though the global incidence of measles is declining, in recent years that decline has slowed (\autoref{fig:trendincidence}) and immigration rates to New Zealand have risen (\autoref{fig:travel}). This suggests that the risk of measles importation could stay at similar levels or increase, though further analyses are required to understand the interaction between these variables.  Of note, however, is the clear seasonality in immigration and travel (\autoref{fig:travel}).  This seasonality suggests that there may be period of increased risk of measles importation, though again the interactions with seasonal measles transmission from the nations of origin will be an important factor in determining the risk of measles importation. Of interest is the asynchrony, or lack of phase, between peak non-New Zealander immigration and New Zealanders travelling. The Christmas summer period being an exception to this, when there is substantial travel by New Zealanders; combined these lead to a very sharp peak in travel rates in December (\autoref{fig:travel}).

@@

The distribution of the measles cases (\autoref{fig:ageandvac}) appears to reflect the distribution of na\"{\i}ve individuals in the population (\autoref{fig:naive_yob}). However, there is some discrepancy between the year of birth of cases (\autoref{fig:yearandvac}) and the proportions na\"{\i}ve (\autoref{fig:naive_yob}), which may reflect other processes like spatial effects in contact rates and therefore measles transmission. The vaccination history of the cases suggests that lack of vaccination cover is the main contributor to the outbreak, though it is noticeable that a proportion ($>16\%$) of cases had been vaccinated at least once. However, the majority of these received only one vaccination (82\%), and were vaccinated when they were young (44\% of those cases vaccinated once were 15 months or younger, see \autoref{fig:vaccstat} and \autoref{fig:vaccstat_close}).

>>>>

\begin{figure}[H]
     \begin{center}
     \includegraphics[width=1\textwidth]{nzers.pdf}
     \end{center}
     \caption{Trends in international travel, determined by immigration and non-New Zealander arrival data and New Zealander travel departure destinations. Note this is for all age categories.}
     \label{fig:travel}
\end{figure}

Though the global incidence of measles is declining, in recent years that decline has slowed (\autoref{fig:trendincidence}) and immigration and non-New Zealand national travel rates to New Zealand have risen (\autoref{fig:travel}). This suggests that the risk of measles importation could stay at similar levels or increase, though further analyses are required to understand the interaction between these variables.  Of note, however, is the clear seasonality in immigration and travel (\autoref{fig:travel}).  This seasonality suggests that there may be period of increased risk of measles importation, though again the interactions with seasonal measles transmission from the nations of origin will be an important factor in determining the risk of measles importation. Of interest is the asynchrony, or lack of phase, between peak non-New Zealander immigration and travel and New Zealanders travelling. The Christmas summer period being an exception to this, when there is substantial travel by New Zealanders; combined these lead to a very sharp peak in travel rates in December (\autoref{fig:travel}).

@@

The distribution of the measles cases (\autoref{fig:ageandvac}) appears to reflect the distribution of na\"{\i}ve individuals in the population (\autoref{fig:naive_yob}). However, there is some discrepancy between the year of birth of cases (\autoref{fig:yearandvac}) and the proportions na\"{\i}ve (\autoref{fig:naive_yob}), which may reflect other processes like spatial effects in contact rates and therefore measles transmission. The vaccination history of the cases suggests that lack of vaccination cover is the main contributor to the outbreak, though it is noticeable that a proportion ($>16\%$) of cases had been vaccinated at least once. However, the majority of these received only one vaccination (82\%), and were vaccinated when they were young (44\% of those cases vaccinated once were 15 months or younger, see \autoref{fig:vaccstat} and \autoref{fig:vaccstat_close}). Those `vaccine failures' in the young may be for a number of reasons, including that vaccine delivery would have been successful, but that infection occured prior to the development of immunity. Furthermore, a number of the `vaccine failures' had been vaccinated by both MMR1 and MMR2 prior to their first birthday, which is against recommended protocol.
